Main text : Effect of copula on extinction risk

### 2019-03-01 MainText.Rmd
minor change

       - 6 Density-dependence models with extreme tail dep. in noise (local/ global dispersal)
           - extrisk depends on tail dependnece as well as on model parameters (under-compensatory, over-compensatory)
           - Rescue effect ??
           - H0 : switching occurs near rc (without dispersal)

@@

 <!--FIG : all nonlinear model results with d=0, extrisk vs. r-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=5 cm]{./Results/ricker_scl_1/ricker_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/hassell_scl_1/hassell_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf}\\
\caption{Transition of higher to lower extinction risk (calculated after $25$ years) for 
the metapopulations affected by extreme left tail dependent noise across
$5$ multiple patches without dispersal ($d=0$), as intrinsic 
growth rate ($r$) goes from under to over-compensatory regime. Opposite trends
was observed with extreme right tail dependent noise.
Error bars represent the standard errors associated with $10000$
simulations for extinction risk computed at each $r$.
\label{fig_extrisk_d0}}
\end{center}
\end{figure*}

>>>>

       - 6 Density-dependent models with extreme tail dep. in noise (local/ global dispersal)
           - extrisk depends on tail dependnece as well as on model parameters (under-compensatory, over-compensatory)
           - Rescue effect ??
           - H0 : switching occurs near rc (without dispersal)

@@

 <!--FIG : all nonlinear model results with d=0, extrisk vs. r-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=5 cm]{./Results/ricker_scl_1/ricker_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/hassell_scl_1/hassell_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/pennycuick_scl_1/pennycuick_extrisk_d0.pdf}\\
\vspace{-0.6 cm}
\includegraphics[width=5 cm]{./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf}
\includegraphics[width=5 cm]{./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf}\\
\caption{Transition of higher to lower extinction risk (calculated after $25$ years) for 
the metapopulations affected by extreme left tail dependent noise across
$5$ multiple patches without dispersal ($d=0$), as intrinsic 
growth rate ($r$) goes from under to over-compensatory regime. Opposite trend
was observed with extreme right tail dependent noise.
Error bars represent the standard errors associated with $10000$
simulations for extinction risk computed at each $r$. Dotted line represents the value of $r$
for each model where their deterministic analog switches from under- to over-compensatory dynamics.
\label{fig_extrisk_d0}}
\end{center}
\end{figure*}
